\section{Introduction}
\label{sec:introduction}

% Maximum 3-4 pages, all external statements must be referenced
% 1. What is the problem in general terms? Why is it important/of interest?
% 2. What other solutions are available? Why are they not good enough? What would we ideally want to have? (-> Narrow down to solutions similar to the last question (i.e. what we ideally want to have), which will be close to our proposition.)
% 3. What are these good similar solutions? How do they work? (some technical insight) What are their limitations?
% 4. What are we proposing? How does it contribute/improve? What do we base our work on, briefly how do we solve?
% 5. What are the assumptions we make? A bit more about the method, what will be presented.

...

% 1. What is the problem in general terms? Why is it important/of interest?

Film photography is a popular medium for capturing images due to its unique visual characteristics which produces a distinct look that is difficult to replicate with digital cameras. Film images have a unique grain pattern, color palettes, and a halation effect around light sources. These visual effects are the result of complex physical properties of film, such as its chemical properties and the way that lightwaves interact with the light-sensitive particles in the film strip. Aestetically and artistically people enjoy the look of film photography, but the process of acquiring film and developing it is time consuming and expensive. Additionally, the development of a given film exposure is not guaranteed to be successful and there is a time delay between taking the photo, bringing the film to a darkroom for development, and finally seeing the result.

Therefore, there is a need for a digital solution that can recreate the visual effects of film photography in real-time. This would allow for the rapid and easy creation of film-like images without the need for expensive film development. Such a solution would be useful for photographers who want to experiment with film photography without the cost and time commitment of developing film. 

% 2. What other solutions are available? Why are they not good enough? What would we ideally want to have? (-> Narrow down to solutions similar to the last question (i.e. what we ideally want to have), which will be close to our proposition.)

Available solutions for recreating film affect involve directly expressing the physical properties of film using statistical models. By modelling pixel patterns of noise, halation, and color distortions, one can directly attempt to recreate the visual effects of film. Such approaches like \cite{film-grain-rendering} have been proposed to model the grain and noise patterns of film using physically realistic models. Grain is then rendered using a Monte Carlo simulation to determine the output of each pixel.

However, directly encoding the visual effects of film is difficult because the visual effects of film are the result of a complex interplay of physical processes. Cinestill 800T film, like most film formats, is a sheet of plastic coated with a layer of light-sensitive silver hallide crystals. When light enters the camera and hits the film, the particles react to the light and create a latent image. The film is then developed in a darkroom using a series of chemical baths which react with the particles in the film to create a visible image. The visual effects of film are therefore the result of complex physical processes involving that are difficult to capture with simple mathematical models.

Even if accurate mathematical models of film grain, halation, and color hue are defined, using such models to directly process each pixel in an image is computationally expensive and slow. The results of partial models of film grain such as CITE RANDOM DOT MODEL are not always visually pleasing. A high quality digital image with pixel dimensions on the order of thousands would require on the order of several minutes to process with direct pixel manipulation. CITE SOMETHING

Ideally, a digital image could be processed into its film equivalent on the order of seconds to acheive results that are visually pleasing and indistinguishable from a true film image. This would allow for the rapid and easy creation of film-like images without the need for expensive film development.

Only visual film affects which are understood from first principles and can be modeled with closed-form statistical models can be encoded directly. Deep learning models have the ability to learn complex mappings and patterns not necessarily perceivable by the human visual system. Thus, one can hope that a deep learning model could achieve results which appear more authentic to the human eye. However, the problem of recreating film affect has not been directly addressed by deep learning literature. Related computational photography problems include camera raw-to-raw mappings, quality enhancement, and style transfer. As none have been directly applied to the problem of film affect, we examined the techniques employed and whether they could be efficiently adapted to the problem of recreating film affect.

% 3. What are these good similar solutions? How do they work? (some technical insight) What are their limitations?

We reviewed approaches to building image-to-image translation models for a variety of tasks, including style transfer, camera raw-to-raw mapping, and image quality enhancement. 

Image quality enhancement models are often trained on paired datasets, where the input image is a low quality image and the output image is a high quality image taken of the same exact scene. Approaches such as \cite{DSLR-quality} involve training image-to-image translation on paired datasets often use CNN architectures with skip connections. These models are trained to minimize the pixel-wise loss between the input image (a low quality image) and the output image (a higher resolution image). 

Mapping one camera model's raw output to another model's output with image-to-image models such as \cite{raw-to-raw} involve training CNN encoder-decoder blocks for different camera models, each trained on respective datasets of images taken by the specific camera. A paired dataset is used to learn the mapping from the latent space representation of one camera's autoencoder to the to the latent space of the another using a latent space normalization technique. 

Style transfer, which maps the visual textures of a style image (such as a painting with long brush strokes) to a content image (such as a photograph), has been successfully applied to a variety of artistic and photographic tasks. Style transfer is often implemented using a deep neural network which is trained to minimize the content loss between the content image and the output image, and the style loss between the style image and the output image. Such approaches include \cite{scaling-painting-style-transfer} and \cite{deep-photo-style-transfer}. Unfortunately for our use-case, style transfer must run an optimization process in order to produce a single output film image from a digital image. This optimization process is slow and doesn't satisfy our requirement of real-time processing. Often, the desired style characteristics must be captured in one input image which is fed into the model. In the case of Cinestill 800T film affect, it is difficult to capture all the visual characteristics of the film in a single exposure. Therefore, style transfer is not best suited for task.

% 4. What are we proposing? How does it contribute/improve? What do we base our work on, briefly how do we solve?

We propose a Unet-like architecture trained on a paired dataset of digital and Cinestill 800T photographs of the same scene, captured at the same angle with a fixed tripod. Digital images are captured on G Sony camera with a 40mm lens with mostly F8 aperture and automatic shutter speed. Cinestill 800T film images were captures on a Nikon F3 camera with a 55mm lens with mostly F8 aperture and automatic shutter speed as well. For very bright scenes, aperture was adjusted up to F32. The dataset was captured in a variety of lighting conditions, including indoor and outdoor scenes around Lausanne, Switzerland. Due to imperfectly aligned digital and film image pairs and the difference in lens widths, we performed image alignment and luminance histogram matching of pairs to preprocess the dataset. 

% 5. What are the assumptions we make? A bit more about the method, what will be presented.

We restrain this work to only solutions involving deep learning. Assuming that the task of recreating film visual affects can be accomplished using purely learning methods, we set out to explore the feasibility of this approach. We acknowledge that the combination of deep learning approaches with direct statistical models of film grain, halation, and color hue may be an overall more effective approach, but we do not explore this in this work. We present our dataset, model architecture, training process, and results in the following sections.