\section{Literature Review}
\label{sec:literature-review}

% All your statements must be referenced. Any related paper/resource you found should be listed for readers.}

% Go over the entire related literature. Start from general to the most specific related methods.

% For the most related papers, and for all papers/algorithms used in your
% project, you should go more into details and explain what the paper does,
% adding an explanation of their pros and cons and how they compare/relate to
% what you have done in your own work.

Many methods have presented as viable solutions for stylistic effect generation using image to image translation using Deep Learning. Among these, there is a variety of kinds of model architectures and effects produced for different stylistic purposes.

\vspace{5pt}\noindent\textbf{Image Translation with GANs.} GANs have seen successful application in the Image to Image domain, such as in Conditional Image-Image Translation \cite{conditionalgan} in which a loss is learned by a discriminator network which is condition on the input. This is further expanded to unpaired image data using Cyclic GANs \cite{cyclicgan} where the translator attempts to replicate the distribution seen in the training set. Two translation networks are used, one in either direction, and cyclic consistency is enforced using the loss function. The authors claim that this allows the model to learn a sensible mapping between the two domains without the need for a large library of paired data.

\vspace{5pt}\noindent\textbf{PreTraining Image to Image Translation Models.} Given that image-to-image translation tasks often benefit from paired input-output image datasets, which are difficult to find or collect, \cite{translation-pretraining} presents a large pretrained model with the capability to model complex scenes and capture the whole natural image distribution. This pretrained model is then able to assist with variety of downstream tasks, such as mask-to-image, sketch-to-image and geometry-to-image translations. The authors propose a pretrained diffusion model \textcolor{red}{Maybe explain diffusion model -- gets quite complicated and abstract in the paper -- @Pierre I'm not sure how useful this paper is for informing our approach and I'm inclined to take it out, so I'll leave this brief section as-is and leave it to your judgment}

\vspace{5pt}\noindent\textbf{Style Transfer.} Style transfer, which maps the visual textures of a style image (such as a painting with long brush strokes) to a content image (such as a photograph), has been successfully applied to a variety of artistic and photographic tasks. Style transfer is often implemented using a deep neural network which is trained to minimize the content loss between the content image and the output image, and the style loss between the style image and the output image. Such approaches include \cite{scaling-painting-style-transfer} and \cite{image-style-transfer} by Gatys et al and \cite{deep-photo-style-transfer} which builds off of the former. Unfortunately for our use-case, style transfer must run an optimization process in order to produce a single output film image from a digital image. This optimization process is slow and doesn't satisfy our requirement of real-time processing. Often, the desired style characteristics must be captured in one input image which is fed into the model. In the case of Cinestill 800T film affect, it is difficult to capture all the visual characteristics of the film in a single exposure. Therefore, style transfer is not best suited for task.

\vspace{5pt}\noindent\textbf{Raw to Raw Mapping.} Mapping one camera model's raw output to another model's output with image-to-image models such as \cite{raw-to-raw} involve training CNN encoder-decoder blocks for different camera models, each trained on separate datasets of images taken by the respective camera type. A paired dataset is used to learn the mapping from the latent space representation of one camera's autoencoder to the to the latent space of the other. A latent space normalisation is used to encourage the encoder-decoder blocks to learn a meaninfully similar latent space representation on the same scene. An analgous architecture with two encoder-decoder blocks trained on unpaired digital and film dataset, alongside a paired dataset could be used to map digital images to generated film equivalents.

\vspace{5pt}\noindent\textbf{Super Resolution.} The task of image super-resolution involves increasing the resolution of a low quality image to a higher resolution. Existing approaches either train on paired datasets of low resolution and high resolution images of the same scene, or a dataset of high resolution images with their downsampled low-quality versions.

Generally, CNN-based methods for super resolution involve downsampling a high-resolution before feeding it through a CNN which involves both convolutional layers and upsampling layers. Often loss is defined based on the L1 or L2 norm between the original high resolution image and the upsampled output image. Training with loss based on average distance metrics between high quality and low quality images tends to produce a blurring affect, as noted in \cite{photo-realistic-super-resolution} and \cite{dslr-quality}. Success of a super resolution model is often measured by the Peak Single to Noise Ratio (PSNR), which is directly optimized by simple MSE losses. In \cite{dslr-quality} different loss functions are employed which combine analytical content and color losses with an adversarially learned texture loss. 

To avoid the challenge of producing perceptually good results with CNNs, approaches such as \cite{pulse-super-resolution} and \cite{photo-realistic-super-resolution} use Generative Adversarial Networks (GANs). In this case, a generative model is trained to produce high resolution images based on low-quality images that are able to fool discriminator trained to distinguish super-resolved images from real images.

\vspace{5pt}\noindent\textbf{Image Colorisation.} Image colorisation involves converting a greyscale image to a colorful version, a task which is very unconstrained and solutions often involve human guidance or input e.g., labeling or scribbling on the image. Without human guidance, closely related example images are instead used by models to map color as in \cite{large-scale-colorisation}. Color palettes for different real-world scenes vary greatly. To address the challenge of finding colorful reference images for a given greyscale, papers \cite{intrinsic-colorisation}, \cite{deep-colorisation}, and \cite{semantic-colorisation} use filtering methods over internet images to select appropriate reference images. Colorisation model outputs are often passed through histogram correction to result in realistic dynamic ranges as in \cite{large-scale-colorisation}. With film photography, the scene's lighting conditions greatly affect which visual affects of Cinestill 800T are most prominent. Therefore an extension of our work could involve making our film-affect mappings semantically-aware. 
