\subsection{Loss Functions}
\label{subsec:loss-functions}

The main difficulty of the task is to design a loss function that captures the perceptual quality of the generated film images, with a special focus on the visual effets that we aim to achieve. Only if our loss function is correctly designed, the model will be able to learn the desired features. As it is difficult to define a single loss function that captures all the desired features, we propose a combination of loss functions that capture various aspects of the image quality. First, we will discuss the individual loss functions, and how we combine them.

\textbf{MSE/ MAE.} Both the mean squared error (MSE, Eq.~\ref{eq:mse}) and mean absolute error (MAE, Eq.~\ref{eq:mae}) are common pixel-to-pixel loss functions, that are popularly used in image reconstruction tasks. They measure the average squared or absolute difference between the predicted and ground truth images pixels, respectively. For two images, $I, J \in \mathbb{R}^{3 \times H \times W}$, the MSE loss is defined as

\begin{equation}
    \mathcal{L}_\text{MSE}(X, Y) = \frac{1}{n} \sum_{i=1}^{n} (X_i - Y_i)^2,
    \label{eq:mse}
\end{equation}

and we equivalently define the MAE loss as

\begin{equation}
    \mathcal{L}_\text{MAE}(I, J) = \frac{1}{n} \sum_{i=1}^{n} |X_i - Y_i|,
    \label{eq:mae}
\end{equation}

where the subscript $i$ indexes the pixels of the images. We hypothesise that
such loss functions are useful in preserving the overall structure of the image,
but are not sufficient to capture higher-level visual effects such as grain and
halation.

\textbf{VGG Loss.} The VGG loss computes the MSE (Eq.~\ref{eq:mse}) between the feature representations of the predicted and ground truth images when passed through a pre-trained VGG-19~\cite{vgg} convolutional network. Letting $\varphi_k(I)$ denote the feature maps of the $k$-th layer of the VGG network, and the set $K$ and $\lambda_k$ denote the layers of interest and their respective weight in the loss function, the VGG loss is defined as

\begin{equation}
   \mathcal{L}_\text{VGG}(I, J) = \sum_{k \in K} \lambda_k \mathcal{L}_\text{MSE}(\varphi_k(I)_i - \varphi_k(J)_i).
    \label{eq:vgg}
\end{equation}

Intuitively, the VGG loss encourages the model to generate images that are similar to the ground truth images in terms of their high-level semantic, such 
as edges, textures, and patterns.

\textbf{Color Loss.} Inspired by~\cite{DSLR-quality}, we consider an alternative to the MSE loss, which we refer to as the color loss. The color loss is a computes the MSE between two images, $X_b$ an $Y_b$, where $X_b$ and $Y_b$ are the blurred versions of the predicted and ground truth images, respectively. We can write

\begin{equation}
    \mathcal{L}_\text{Color}(X, Y) = \mathcal{L}_\text{MSE}(X_b, Y_b).
    \label{eq:color}
\end{equation}

As the authors of the original paper argue, the main idea behind the loss is to evaluate the brighness, contrast and major colours of the image while ignoring fine-grained texture and content comparison. Crucially, the color loss, unlike MSE or MAE, is more robust to small pixel shifts which are present in our training data. However, as a standalone loss we hypothesise that the color loss is not sufficient to preserve details or high-level visual effects in the image.

\textbf{Total Variational Loss.} Traditionally, the total variational loss is used to encourage image smoothness and reduce noise by minimising the sum of the absolute differences between shifted pixel values.

In our particular case, we aim to create grain, which can be seen as some form of noise. To this end, we propose two variants of the total variational loss which we term the absolute total variational loss and the relative total variational loss.

The absolute total variational loss (Eq.~\ref{eq:tv-abs}) is defined as the inverse
of the total variation of the predicted image. Hence, by minimizing the absolute
total variational loss, we maximise the noise produced in an image. 

\begin{equation}
    \mathcal{L}_\text{TV-Abs}(X) = 1 / \text{TV}(X)
    \label{eq:tv-abs}
\end{equation}

The relative total variational loss (Eq.~\ref{eq:tv-rel}) is defined as the
absolute difference between the total variation of the predicted and ground
truth images. This loss encourages the model to generate images with a similar
amount of noise to the ground truth film images.

\begin{equation}
  \mathcal{L}_\text{TV-Rel} = |TV(X) - TV(Y)| 
  \label{eq:tv-rel}
\end{equation}

\textbf{Combination of Losses.} We combine the individual loss functions to form the final loss function using weighted sum. For a set of weights $beta_i$ and loss functions $\mathcal{L}_i$, the final loss function is defined as

\begin{equation}
    \mathcal{L}(X, Y) = \sum_{i} \beta_i \mathcal{L}_i(X, Y).
    \label{eq:combined-loss}
\end{equation}

Some combinations of loss functions are more effective than others, and we will experiment with different combinations, as outlined in section \ref{subsec:experiments}.

% \textbf{CoBi Loss.} Introduced by \cite{zoom-to-learn}, Contextual Bilateral Loss (CoBi Loss) is inspired by the bilateral filter \cite{bilateral-filter} which preserves-edges while reducing noise. The motivation for its design is to judge image feature similarity even when an image pair is misaligned. CoBi Loss combines spatial pixel coordinates and pixel-level RGB information for a nearest neighbor search on image features. 
% 
% \begin{definition}
%   \textbf{CoBi Loss}
% \begin{equation}
%   \text{CoBi}(P, Q) = \frac{1}{N}\Sigma_{i,j}\min_{j=1,...M} (D_{p_i,q_i} + \omega_s D'_{p_i, q_i})
% \end{equation}
% \end{definition}
% 
% Where $P$ and $Q$ are the predicted and ground truth images with $N$ and $M$ feature points respectively. $\omega_s$ is a hyperparameter that controls the influence of the spatial awareness for nearest neighbor search. $D_{p_i,q_i}$ and $D'_{p_i,q_i}$ are distance measurements between feature points of the predicted and ground truth images. 

% TODO: Talk about combination of losses.