\subsection{Model}
\label{subsec:model}

Our image style translation network is based on the U-Net
architecture~\cite{unet}. U-Net is a type of convolutional neural network (CNN)
originally introduced for image segmentation tasks in 2015. Since, it has been
successfully adapted for various image-to-image translation tasks and is a
building block of many modern model families, such as GANs or Diffusion models
\textit{(CITE)}. The network features a U-shaped architecture, composed of a a
contracting path (encoder) and an expansive path (decoder). The contracting path
resembles a conventional convolutional network, involving repeated convolutions
followed by a non-linear activation functions and pooling operations. This path
progressively reduces spatial dimensions while enhancing feature details.
Conversely, the expansive path integrates both feature and spatial information
using up-convolutions and by merging with high-resolution features from the
contracting path via skip connections.

% Motivation for using U-Net
The architecture is well-suited for our problem for multiple reasons: First, it
is a relatively simple and well-understood model family, allowing us to focus on
the specifics of our problem rather than the intricacies of the model. Second,
despite its simplicity, it has been shown to be effective for image-to-image
translation tasks related to our task at hand, such as \textit{CITE}. Finally,
in being fully convolutional, it can be applied to images of arbitrary size
\footnote{So long as the input dimensions are divisible by $2^L$, where $L$ is
the number of layers in the contracting path}.  This allows us to experiment
with training on smaller image patches and applying the network to larger images
at test time with no architectural changes or pre-processing steps.

% TODO: Maybe add some more citations on related work using U-Net

% TODO: Add figure for U-Net architecture

% Detailed model architecture
For our experiments we follow related work~\cite{unet,DSLR-quality,raw-to-raw}
to set sensible hyperparameters for our model. Our image style translation
network is fully convolutional, with a three-layer contracting and expansive
path. The contracting path consists of three convolutional blocks with 64, 128,
and 256 filters, respectively. Each block consists of two convolutional layers
with 3×3 kernels and zero padding, interleaved with ReLu activation functions.
In between each of the convolutional blocks, we downsample the spatial dimension
of the feature maps by a factor of two using a 2×2 max-pooling operation. The
expansive path performs the reverse operation, i.e. it upsamples the spatial
dimension and decreases the number of filters from 256 to 128, 64, and finally
to 3. Upsampling is performed via a 2×2 transposed convolution. After
upsampling, we concatenate the feature maps from the corresponding layer in the
contracting path before applying the convolutional block. After the final layer,
the model outputs a three-channel image, corresponding to the RGB channels of
the transformed image.  Hence, the overall translation network $F_{\theta}$ thus
is an image-to-image model, that takes an image $I$ as input and outputs a
transformed image $F_{\theta}(I)$. Both input and output are three-dimensional
tensors of size $3 \times H \times W$, where $3$ correspond to the RGB channels
and $H$ and $W$ are the height and width of the image, respectively. The total
number of parameters in the model is approximately 1.9M, corresponding to a
memory footprint of around 7.6MB.

% TODO: Maybe mention that we don't employ normalisation/ dropout layers

% \begin{table}{ccc}
%     \centering
%     \caption{
%         \textbf{Model architectures.} The table shows the base model architecture that is used for all experiments, unless otherwise specified.
%     }
%     \label{tab:model}
%     \begin{tabular}{ccc}
%         \toprule
%         \# Input Channels & \# Hidden Channels & Convolution & Pooling & Non-Linearity \\
%         3 & 64, 128, 256 & 3x3 (1) & 2x2 Max & ReLU \\
%         \midrule
%         \bottomrule
% \end{table}